---
output: github_document

references: 
- id: ARHT2016
  title: An adaptable generalization of Hotelling's  $T^2$ test in high dimension
  author: 
  - family: Li
    given: Haoran
  - family: Aue
    given: Alexander
  - family: Paul
    given: Debashis
  - family: Peng
    given: Jie
  - family: Wang
    given: Pei
  publisher: arXiv preprint arXiv:1609.08725
  issued:
     year: 2016 
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ARHT

Perform the Adaptable Regularized Hotelling's $T^2$ test (ARHT) proposed by @ARHT2016. Both one- and two- sample mean test are available with various probabilistic alternative prior models. It contains a function to consistently estimate higher order moments of the population covariance spectral distribution using the spectral of the sample covariance matrix. In addition, it contains a function to sample from 3-variate chi-squared random vectors approximately with a given correlation matrix when the degrees of freedom are large. 

## CRAN download counts
[![](https://cranlogs.r-pkg.org/badges/ARHT)](https://cran.r-project.org/package=ARHT)

## Installation

You can install ARHT from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("HaoranLi/ARHT")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ARHT)
## basic example code
set.seed(10086)
# One-sample test
n1 = 300; p =500
dataX = matrix(rnorm(n1 * p), nrow = n1, ncol = p)
res1 = ARHT(dataX)

# Two-sample test
n2= 400
dataY = matrix(rnorm(n2 * p), nrow = n2, ncol = p )
res2 = ARHT(dataX, dataY, mu_0 = rep(0.01,p))

# Specify probabilistic alternative priors model
res3 = ARHT(dataX, dataY, mu_0 = rep(0.01,p), 
            prob_alt_prior = list(c(1/3, 1/3, 1/3), c(0,1,0)))
# Change Type 1 error calibration method
res4 = ARHT(dataX, dataY, mu_0 = rep(0.01,p),
            Type1error_calib = "sqrt")
RejectOrNot = res4$ARHT_pvalue < 0.05
```

## Reference

